An exploratory analysis of changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh

### 2020-10-05 Frequency-of-Travel-by-Mode-COVID-19-Bangladesh/Frequency-of-Travel-by-Mode-COVID-19-Bangladesh.Rmd
Survey description added. proofread by shaila

To understand the transitions towards different trip-making frequencies more clearly, including possible adaptations by mode, we convert the cross-tabulations to probability transition matrices, which we then visualize using circular plots.

>>>>

To more clearly understand the transitions towards different trip-making frequencies, including possible adaptations, we convert the cross-tabulations to probability transition matrices, which we then visualize using circular plots.
